Breanna_Code

### 2022-09-29 Draft_Report.Rmd
added ggplots

```{r load_packages}
library(dplyr)
library(lme4)

@@

@@

```{r plot_histograms}
par(mfrow=c(2,4))

@@

###Asses if trends are reasonably linear

```{r plot_stuff}
Metrics %>%

>>>>

```{r load_packages}
library(dplyr)
library(lme4)
library(tidyverse)

@@

```{r data_dictionary}
#Putting a data dictionary here in case it is useful
dict=data.frame(longName=names(Metrics), shortName=c("Station", "Abundance", "Richness", "Biomass", "Diversity", "Evenness", "SDI", "Ax_Staining", "Year", "Rep", "Distance", "Direction"))

#new data file with short names for playing
metrics <- Metrics %>%
  mutate(DiffuserDirection=ifelse(DiffuserDirection==1, "upstream", "downstream"))
names(metrics)=dict$shortName
```

@@

```{r histograms with ggplot}
metrics %>% 
  select(!c('Direction', 'Distance')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year'), names_to="Indicator", values_to="value") %>%
  ggplot(aes(x=value)) +
    geom_histogram()+
    facet_wrap(~Indicator, scale="free_x")

```{r plot_histograms}

par(mfrow=c(2,4))

@@

###Asses if trends are reasonably linear
Here we should be plotting response variables against predictors.

### Distance
Definitely some trends with distance,  but also definitely some non-linear things happening

```{r scatterplots in ggplot}
#Distance scatterplot

metrics %>% 
  select(!c('Direction')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year', 'Distance'), names_to="Indicator", values_to="value") %>%
  ggplot(aes(x=Distance, y=value)) +
    geom_point()+
    facet_wrap(~Indicator, scale="free_y")

### Direction

```{r scatterplots in ggplot}

metrics %>% 
  select(!c('Distance')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year', 'Direction'), names_to="Indicator", values_to="value") %>%
  ggplot(aes(x=Direction, y=value)) +
    geom_boxplot()+
    facet_wrap(~Indicator, scale="free_y")

```{r plot_response_v_predictor}
# these are a good use of pipes, but don't give us an easy way to assess for linearity in the key variables. 
Metrics %>%
